---
title       : Vehicle Performance by Number of Cylinders
subtitle    : HTML5 Slides from R Markdown (Slidify)
author      : Shang Ju
job         : Oct 13, 2016
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Hypotheses (Myths) about Cars

1. More Cylinders    ==>      Fast Cars
2. Fast Cars         ==>      High Fuel Consuption
3. High Horsepower   ==>      Fast Cars

We will do a simple test on the above hypotheses by analyzing the built-in R dataset "mtcars".

---

## Introduction of Source Data (datasets::mtcars)

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r}
str(mtcars)
```

--- 

## Conclusion in a Nutshell

We found positive correlation between the number of cylinders and the horsepwer.

We also found that faster cars tend to have high horsepower, but not necessarily high miles-per-gallon. This is probably because faster cars (sport cars) tend to be lighter in weight, thus require less gasoline to accelerate.

---

## Find the Answers Yourself!

Go to [findshawn.shinyapps.io/mtcars](https://findshawn.shinyapps.io/mtcars) and play with the interactive graph yourself, and see if you can draw your own conclusions!

```{r echo = FALSE, fig.width = 10, fig.height = 5}
library(ggplot2)
mtcars$model <- row.names(mtcars)
ggplot(data = subset(mtcars,cyl == 4),aes(x = mpg, y = hp, label=model)) +
    labs(x = 'Miles per Gallon', y = 'Horsepower', colour = '1/4 mile time',size = 'Weight (1000 lbs)') +
    theme(text = element_text(size=16)) +
    geom_label(aes(fill = qsec,check_overlap = TRUE), colour = "white", fontface = "bold",vjust="inward",hjust="inward") +
    scale_fill_gradient(high = 'blue',low = 'cyan2',name = "1/4 mile time (s)")

```

